\chapter{Communication Systems}

\input{gfc/comm-Intro}

\section{Earth-to-Orbiter}

\input{gfc/comm-deepSpace}

\input{laser-communication}

%This is surface-to-orbiter subsection
\input{Communication/CommRasmus}

\input{gfc/comm-Pen2Surf}	

%\section{Probe-to-Penetrator}

%\subsection{High Directional Link}

\input{DirectionalLink} %Isn't this supposed to be a subsection of the penetrator to lander link?

\autsection{Communication Systems Proposal}{Kristian Sloth Lauszus, Rasmus Lundby Pedersen, and Gustavo Feijóo Carrillo}

==== Trans Ice Communications Presentation
    -Fiber optical cables are heavy.
    -Repeaters require RTGs with a high interval. Number of repeaters is highly depending on ice conditinos
    -One-to-one communication link through the ice is a better alternative.
CONCLUSION: Fiber optical cable is not a good option, cable is going to be enormous.
            One-to-one communication must be researched further - more details are required.
            Repeater communication must be researched further.
            
==== Communications Presentation
-Ice link:
-Surface relay:
-Ground control link:
One-to-one communication, assuming poor ice conditions, link is possible
Surface to orbiter. Small tracking possibilities, low gain antenna (LGA) is used.
3m high gain antenna.
CONCLUSION: One-to-one communication must be researched further. More details are needed
            The antenna transmitting down through the ice must be aligned. High risk, as landing site will probably not be flat.

* Repeaters along decent path
	* Increases a lot when introducing salinity
	* Pros:
		* Scalable
	* Cons:
		* Complexity
		* Separate RTGs
	* Too complex
		* Better just use one proper designed unit in the penetrator
		* Might be a combinations of repeaters and a big antenna at the lander and probe
		* Will also work better if the probe doesn't descent in a straight line.

	* Also a combination of repeaters and tether could be used.
	* The repeater will also work better if the penetrator move to the side. Repeaters do not risk breaking like the tether.
	* If one repeater fails the data rate will drop by a factor 10 or more, so we have a little redundancy.
